Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-07 aggregation/agg-semantic.tex
Finishing body revision

Similarly, LCIA method providers should ensure that their methods make use of stable semantic references to elementary flows and contexts.  Current research has revealed widespread challenges to finding consistency on the identities of elementary flows despite the community's longstanding awareness of the problem, and several mutually inconsistent reference flow sets exist \citep{Edelen_2017}.  The conventional understanding of a ``flow'' as comprising a substance and a context together (e.g. methane, emissions to air) causes a combinatorial increase in the number of flows in a database, and also multiplies the potential points of disagreement across sources.  I reiterate Edelen et al.'s (ibid.) suggestion to explicitly regard substances (which can easily include non-material ``flowables'' such as land occupation and transformation) and contexts as independent semantic classes.  In this case, an elementary flow entry in the disclosure item~\ref{itm:em} would require both a flowable and a context.

>>>>

Similarly, LCIA method providers should ensure that their methods make use of stable semantic references to elementary flows and contexts.  Current research has revealed widespread challenges to finding consistency on the identities of elementary flows despite the community's longstanding awareness of the problem \citep{Speck_2015,Herrmann_2015}, and several mutually inconsistent reference flow sets exist \citep{Edelen_2017}.  The conventional understanding of a ``flow'' as comprising a substance and a context together (e.g. methane, emissions to air) causes a combinatorial increase in the number of flows in a database, and also multiplies the potential points of disagreement across sources.  I reiterate Edelen et al.'s (ibid.) suggestion to explicitly regard substances (which can easily include non-material ``flowables'' such as land occupation and transformation) and contexts as independent semantic classes.  In this case, an elementary flow entry in the disclosure item~\ref{itm:em} would require both a flowable and a context.
